Verifying Demonstrations

### 2017-09-28 properties.tex
Clarifies the idea for unpredictable future, adds two more problems

We first introduce something we call a \emph{time-authenticator tag}.
This is an unpredictable value \(\tau_t\) which is published at time \(t\).
The idea is that it is difficult to guess \(\tau_t\) for a given \(t\) in 
advance, i.e.\ the use of \(\tau_t\) must have happened after time \(t\) with 
high probability.

@@

>>>>

The first thing we want to do is to prevent Alice from collecting witnesses for 
a future protest.
For this, we introduce something we call a \emph{time-authenticator tag}.
This is an unpredictable value \(\tau_t\) which is published at time \(t\).
The idea is that it is difficult to guess \(\tau_t\) for a given \(t\) in 
advance, i.e.\ any use of \(\tau_t\) must have happened after time \(t\) with 
high probability.

@@

\begin{definition}[Collision]
  Given tag \(\tau\), probability of collision?
\end{definition}

\begin{definition}[Changing the past]
  Given a witness for time \(t\), change it to time \(t'\).
  \dots
\end{definition}
